Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-08-26 paper/paper.tex
added deterministic data to plot-arrow-ave Tested everything on wentworth.

\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
In general we have found that the deterministic simulations of the
protein reaction sequence discussed above results in robust
oscillatory behavoir of polar selection and oscillation in a wide
variety of cell shapes.  On the other hand, the stochastic simulations
show back and forth behavoir that breaks down in more assymetric
shapes with larger sizes, which is similar to what Mannik has observed
experimentally.

\begin{figure}

  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-520}
  \caption{Arrow plots of our stadium shape}
  \label{stadium-arrow}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../paper/plot-ave}
  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1500-95-stoch}
  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1850-95-stoch}
  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-2500-95-stoch}
  \caption{Arrow plots of our randst shape}
  \label{stadium-arrow}
\end{figure}

>>>>

\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
We have inspected movies made
We have found that the deterministic simulations of the protein
reaction sequence discussed above results in robust oscillatory
behavoir of polar selection and oscillation in a wide variety of cell
shapes.  This differs with Mannik's experimental findings that show
much less regular behavoir, with a large variation in the location of
maxima.  On the other hand, our stochastic simulations show irregular
behavoir in the irregular shapes and more regular, pole to pole
oscillations in the pill and stadium shaped cells.

Figure \ref{randst-plot-ave} shows a comparison of irregular shapes
simulated with the stochastic method and with the deterministic
method, along with a plot taken from Mannik showing the location of
sequential MinD maxima in the experimental cells.  Like Manniks, the
tips of the arrows in our plots show subsequent maxima, and the data
overlays a color plot of time averaged MinD concentration.  These
plots illustrate the adequacy of the stochastic method and inadequacy
of the deterministic one.  The stochastic plots show similar random behavoir to Manniks

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-520}
  \caption{Arrow plots of our stadium shape}
  \label{stadium-arrow}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../paper/plot-ave}
  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1500-95-stoch}
  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1850-95-stoch}
  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-2500-95-stoch}
  \caption{Arrow plots of our randst shape}
  \label{randst-plot-ave}
\end{figure}
